---
title: "Implementation of ridreg regression Class `ridreg` "
author: "Saman and Rabnawaz"
header-includes:
   - \usepackage{statPack}
package: statPack
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Using the caret package and your ridgereg() function to create a predictive model for the BostonHousing data found in the mlbench package.

## The Document should include the following:
- Divide the BostonHousing data (or your own API data) into a test and training dataset using the
caret package.
- Fit a linear regression model and a linear regression model with forward selection of covariates on the training dataset. Information on linear regression models in the caret package can be found here http://topepo.github.io/caret/Linear Regression.html.
- Evaluate the performance of this model on the training dataset.
- Fit a ridge regression model using your ridgereg() function to the training dataset for different
values of . How to include custom models in caret is described here
http://topepo.github.io/caret/custom models.html.
- Find the best hyperparameter value for  using 10-fold cross-validation on the training set. More
information how to use the caret package for training can be found here
https://cran.r-project.org/web/packages/caret/vignettes/caret.pdf and here
http://topepo.github.io/caret/training.html.
- Evaluate the performance of all three models on the test dataset and write some concluding com-
ments.

### 1. Divide the BostonHousing data
```{r, echo=TRUE , results= "hide", warning=FALSE , message=FALSE}
library(mlbench)
library(caret)
library(statPack)
```

### Creating Test and Training Data set
```{r}
data("BostonHousing") #load a data
boston_data <- BostonHousing #set a data to variable
indexes = createDataPartition(boston_data$rm, p = .70, list = FALSE, times = 1)
training<- boston_data[indexes,] #assigninng 70% data to test
testing<- boston_data[-indexes,]  #assigning remaining 30% data to training set

```

### 2. Fit Linear Regression Model and Linear Regression Model with Forward selection

```{r}
set.seed(12345)
ridgereg_fit <- train(rm ~ . , data = training, method = "lm")
print(ridgereg_fit)

ridgereg_forward_fit <- train(rm ~ ., data = training, method = "leapForward")
print(ridgereg_forward_fit)
```

### 3. performance of this model on the training dataset.
to answere here

### 4. Creating Custom Model for Ridge Regression
```{r}
ridge_custom <- list(type=c("Regression"),library="statPack",loop=NULL,prob=NULL)

ridge_custom$parameters <- data.frame(parameter="lambda",class="numeric",label="lambda")

ridge_custom$grid <- function(y,x, len=NULL, search="grid")
{
    if(search == "grid") {
    out <- expand.grid(lambda = c(0, 10 ^ seq(-1, -4, length = len - 1)))
  } else {
    out <- data.frame(lambda = 10^runif(len, min = -5, 1))
  }
  out


}

ridge_custom$fit <- function (x, y, wts, param, lev, last, classProbs, ...)
{
if (is.data.frame(x))
    dat<- x
  else as.data.frame(x)
    dat$.outcome <- y
  result <- ridgereg$new(dat$.outcome ~ ., data = dat, lambda=param$lambda, ...)
  result
}

ridge_custom$predict <- function (modelFit, newdata, submodels = NULL) {
  if (!is.data.frame(newdata))
  {
    newdata <- as.data.frame(newdata)
  }
  modelFit$predict(newdata)
}
# 
# 
# set.seed(12345)
# result <- train( rm ~ ., data=training, method="ridge")
# print(result)

```
### 5.


### 6.

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
