---
title: "Implementation of ridreg regression Class `ridreg` "
author: "Saman and Rabnawaz"
header-includes:
   - \usepackage{statPack}
package: statPack
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Using the caret package and your ridgereg() function to create a predictive model for the BostonHousing data found in the mlbench package.

## The Document should include the following:
- Divide the BostonHousing data (or your own API data) into a test and training dataset using the
caret package.
- Fit a linear regression model and a linear regression model with forward selection of covariates on the training dataset. Information on linear regression models in the caret package can be found here http://topepo.github.io/caret/Linear Regression.html.
- Evaluate the performance of this model on the training dataset.
- Fit a ridge regression model using your ridgereg() function to the training dataset for different
values of . How to include custom models in caret is described here
http://topepo.github.io/caret/custom models.html.
- Find the best hyperparameter value for  using 10-fold cross-validation on the training set. More
information how to use the caret package for training can be found here
https://cran.r-project.org/web/packages/caret/vignettes/caret.pdf and here
http://topepo.github.io/caret/training.html.
- Evaluate the performance of all three models on the test dataset and write some concluding com-
ments.

### Divide the BostonHousing data
```{r}
library(statPack)
library(caret)
library(lattice)
library(ggplot2)
library(mlbench)
```
```{r}

data("BostonHousing") #load a data 
boston_data <- BostonHousing #set a data to variable
indexes = caret::createDataPartition(boston_data$rm, p = .70, list = FALSE, times = 1)
training<- boston_data[indexes,] #assigninng 70% data to test
testing<- boston_data[-indexes,]  #assigning remaining 30% data to training set

set.seed(12345)
ridgereg_fit <- caret::train(rm ~ . , data = training, method = "lm")
# summary(ridgereg_fit)
print(ridgereg_fit)
ridgereg_forward_fit <- caret::train(rm ~ ., data = training, method = "leapForward")
print(ridgereg_forward_fit)
```


### Fit a linear regression model and a linear regression model with forward selection
```{r}
# set.seed(12345)
# ridgereg_fit <- train(rm ~ . , data = training, method = "lm")
# # summary(ridgereg_fit)
# print(ridgereg_fit)
# set.seed(12345)
# ridgereg_forward_fit <- train(rm ~ ., data = training, method = "leapForward")
# print(ridgereg_forward_fit)
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
